Efficient UQ for chemical systems using active \author{Manav Vohra, Alen Alexanderian, Hayley Guy, Sankaran Mahadevan} subspaces

### 2018-07-31 Paper/intro.tex
..

The application problem considered in this work is the
H$_2$/O$_2$ reaction mechanism~\cite{Yetter:1991}. This mechanism has been
gaining a lot of attention in the recent years as a potential source of clean
energy for locomotive applications~\cite{Das:1996}. (\alennote{you say recent years, but
the reference is from 1996, are there more recent papers you can refer to?}.   
The mechanism involves 19
reactions including chain reactions, dissociation/recombination reactions, and
formation and consumption of intermediate species. For each reaction in
table~\ref{tab:kinetics}, the reaction rate is assumed to show an Arrhenius
correlation with temperature:
%
\be
k_i(T) = A_iT^{n_i}\exp(-E_{a,i}/RT), 
\label{eq:rate}
\ee
%
where $A_i$ is the pre-exponent, $n_i$ is the index of $T$, $E_{a,i}$ is the
activation energy corresponding to the $i^{th}$ reaction, and $R$ is the
universal gas constant.

>>>>

The application problem considered in this work is the
H$_2$/O$_2$ reaction mechanism~\cite{Yetter:1991}. This mechanism has gained
a lot of attention as a potential source of clean energy
locomotive applications~\cite{Das:1996}, and more recently in fuel cells~\cite{Loges:2008}. 
The mechanism involves 19
reactions including chain reactions, dissociation/recombination reactions, and
formation and consumption of intermediate species. For each reaction in
table~\ref{tab:kinetics}, the reaction rate is assumed to show an Arrhenius
correlation with temperature:
%
\be
k_i(T) = A_iT^{n_i}\exp(-E_{a,i}/RT), 
\label{eq:rate}
\ee
%
where $A_i$ is the pre-exponent, $n_i$ is the index of $T$, $E_{a,i}$ is the
activation energy corresponding to the $i^{th}$ reaction, and $R$ is the
universal gas constant.
